\begin{abstract}

Causality analysis on system auditing data has emerged as an important solution for attack investigation.
Given a POI (Point-Of-Interest) like creating a virus file, causality analysis constructs a dependency graph, where nodes represent system entities (\eg processes and files) and edges represent dependencies among entities, to reveal the attack sequences.
However, causality analysis often generates a large graph ($> 100,000$ edges), and thus requires non-trivial efforts of manual inspection.
From the dependency graphs of various attacks, we observe that 
(1) dependencies that are highly related to POI often present a different set of properties (\eg data flow and time) than less-relevant dependencies;
(2) POI is often related to a few sources (represented as entry nodes on the graph).
Thus, to address the challenges,
%faced by causality analysis, 
we propose \tool, a novel framework that identifies the critical component of a dependency graph by assigning discriminative weights to dependencies for distinguishing relevant dependencies from less-relevant dependencies, and computing relevance scores based on the dependency weights to identify relevant sources. 
In particular, \tool performs forward causality analysis from the top-ranked sources to filter out edges that are not found in the 
%forward causality analysis
graph overlap, preserving only edges that are highly relevant to both POI and relevant sources.
Our evaluations on the real system auditing data of 10 attack cases show that
%on average, 
\tool can reduce the large dependency graphs ($\sim 700,000$ edges) to a small graph ($\sim 200$ edges), achieving $96\%$ reduction rate on average.
Such results demonstrate the effectiveness of \tool in filtering out irrelevant dependencies and preserving attack-relevant information.


%with only $8\%$ loss of relevant dependencies.


\end{abstract}